---
title: "Free-to-Paid Conversion Analysis"
author: "Guy Mor"
date: "2025-05-04"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
query <- readLines("queries/engagement_metrics.sql")
```

```{r}
cat(query, sep = "\n")
```

```{r}
result <- data.frame(
  conversion_rate = 11.29,
  av_reg_watch = 3.42,
  av_watch_purch = 26.25
)

knitr::kable(result, caption = "Summary of Student Engagement Metrics")
```

## Interpretation

- **Conversion Rate (11.29%)**:   
Slightly more than 1 in 10 students who engaged with a lecture chose to purchase a subscription. 

- **Average Registration-to-Engagement Time (3.42 days)**:   
Students typically start watching lectures within just a few days after signing up, which may indicate that the platform is easy to use and effectively encourages new users to get started quickly.

- **Average Engagement-to-Purchase Time (26.25 days)**:   
On average, students wait nearly a month after watching their first lecture before subscribing.
This may reflect hesitation or a tendency to wait for special deals before making a purchase.

```{r}
df <- read.csv("data/time_differences.csv")
head(df, 5)
```

```{r}
get_mode <- function(v) {
  v <- na.omit(v)
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}
```

```{r}
df$date_diff_reg_watch <- as.numeric(df$date_diff_reg_watch)
df$date_diff_watch_purch <- suppressWarnings(as.numeric(df$date_diff_watch_purch))


# Registration to Watch
mean_reg_watch   <- mean(df$date_diff_reg_watch, na.rm = TRUE)
median_reg_watch <- median(df$date_diff_reg_watch, na.rm = TRUE)
mode_reg_watch   <- get_mode(df$date_diff_reg_watch)

# Watch to Purchase
mean_watch_purch   <- mean(df$date_diff_watch_purch, na.rm = TRUE)
median_watch_purch <- median(df$date_diff_watch_purch, na.rm = TRUE)
mode_watch_purch   <- get_mode(df$date_diff_watch_purch)

cat("Registration → Watch:\n")
cat("Mean:   ", round(mean_reg_watch, 2), "\n")
cat("Median: ", median_reg_watch, "\n")
cat("Mode:   ", mode_reg_watch, "\n\n")

cat("Watch → Purchase:\n")
cat("Mean:   ", round(mean_watch_purch, 2), "\n")
cat("Median: ", median_watch_purch, "\n")
cat("Mode:   ", mode_watch_purch, "\n")
```


## Interpretation of Distribution Metrics

- **Registration → Watch**  
The mean (3.42 days), median (0 days), and mode (0 days) are all relatively close, suggesting that most users begin engaging with the platform shortly after registering. This indicates a **swift onboarding process** and likely reflects an intuitive and accessible user experience that encourages immediate engagement.

- **Watch → Purchase**  
Although the **median (1 day)** and **mode (0 days)** imply that a majority of users who convert do so shortly after watching their first lecture, the **mean (26.25 days)** is considerably higher. This discrepancy suggests the presence of **outliers**—users who delayed their subscription—pulling the average upward. These delayed conversions may indicate **hesitancy** or a tendency to wait for **special offers or discounts** before purchasing.


```{r}
hist(
  df$date_diff_reg_watch,
  breaks = 30,          
  col = "skyblue",              
  main = "Registration to Watch",
  xlab = "Days",
  ylab = "Number of Students"
)
```

```{r}
hist(
  df$date_diff_watch_purch[!is.na(df$date_diff_watch_purch)],
  breaks = 30,
  col = "lightgreen",
  main = "Watch to Purchase",
  xlab = "Days",
  ylab = "Number of Students"
)
```

## Distribution Insights

Both distributions show that most students take action shortly after the previous step.  
The **Watch → Purchase** distribution has a slightly longer right tail, which may suggest that some students wait before purchasing — possibly due to financial considerations or promotional offers.  
However, the difference between the two distributions is not dramatic, indicating a relatively similar behavioral pattern across both transitions.

## Conclusion

Most users who convert do so quickly after watching a lecture, as shown by the low median and mode.  
However, the higher mean suggests a smaller group delays their purchase, highlighting an opportunity to target these users with tailored follow-up or offers.






















